---
title: "rvesting-movies"
author: "Silas Bamidele"
date: "2023-08-02"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Harvesting IMDB Movies with RVest to include Movie Directors

Get movie titles
```{r}
library(dplyr)
library(stringr)
library(rvest)

url <- "https://imdb.com/chart/top"
top_movies <- read_html(url)   #read the supplied url with read_html -- powered by rvest
top_movies %>% 
  html_nodes("ul.ipc-metadata-list li div.cli-children h3") %>%  #pipe top_movies into html_nodes and html_text 
  html_text() -> top_movies

top_movies %>% 
  str_trim() %>%  
  str_split("\n") -> top_movies   #After trimming and splitting it down, you get a LIST

top_movies %>%  #outputs as a list here, so let's unlist
  unlist() -> top_movies  # after unlisting, you then get a vector of characters, with the movie names

  top_movies %>% 
    str_replace("^\\d+\\.\\s*", "") -> top_movies
  
  top_movies %>% 
    as.character() -> top_movies #type casting
  
  top_movies
  
 
```

Get movie years
```{r}
library(dplyr)
library(stringr)
library(rvest)

url <- "https://imdb.com/chart/top"
top_movies <- read_html(url)   #read the supplied url with read_html -- powered by rvest
top_movies %>% 
  html_nodes("ul.ipc-metadata-list li div.cli-title-metadata") %>%  #pipe top_movies into html_nodes and html_text 
  html_text() -> top_years

top_years %>% 
  str_extract("\\d{4}") -> top_years # extracts the year values from the data

top_years %>% 
  as.integer() -> top_years #type casting to integer

```

Get movie ratings
```{r}
library(dplyr)
library(stringr)
library(rvest)

url <- "https://imdb.com/chart/top"
top_movies <- read_html(url)   #read the supplied url with read_html -- powered by rvest
top_movies %>% 
  html_nodes("ul.ipc-metadata-list li .ipc-rating-star--imdb") %>%  #pipe into html_nodes and html_text -- most important here 
  html_text() -> top_ratings  # returns all ratings in char format. Let's change to numeric

top_ratings %>% 
  as.numeric() -> top_ratings #type casting

top_ratings

```

## Web scrapping for movie directors
Notice on the IMDB website, the director names are on the  single movie pages, that is the movie link has been clicked, as such links are represented by anchor tags, so we'll be targeting the anchor <a href="> tag, and then spilling the hrefs out with the html_attr() function
```{r}
library(dplyr)
library(stringr)
library(rvest)

url <- "https://imdb.com/chart/top"
top_movies <- read_html(url)
top_movies %>% 
  html_nodes("ul.ipc-metadata-list li div.cli-children a") %>%  #target the anchor tag this time 
  html_attr("href") -> hrefs

#use paste0 to concatenate domain name and the resulting hrefs
paste0("https://www.imdb.com", hrefs) -> links #this forms the single page links which are then piped as the new urls to the read_html function -- **this might be the most important concept to grasp here*

links[1] %>% #to test, pipe a single link to read_html and drill down for the director
  read_html() %>% 
  html_node("div.ipc-metadata-list-item__content-container ul.ipc-inline-list--show-dividers li a" ) %>% 
  html_text() -> director #this is a test code to return a single director

#Now to fetch a list of all directors with the lapply loop

lapply(links, function(link){
   link %>% 
  read_html() %>% 
  html_node("div.ipc-metadata-list-item__content-container ul.ipc-inline-list--show-dividers li a" ) %>% 
  html_text() 
  }) -> directors  #returns a list, so let's unlist in the next code chunk

```

```{r}
library(dplyr)
library(stringr)
library(rvest)

directors %>% 
  unlist() -> directors

directors
```

Generating a new tibble to include directors
```{r}
library(tibble)
library(dplyr)
tibble(
  Movies = as.character(top_movies),
  Movie_Years = top_years,
  Ratings = top_ratings,
  Directors = directors
       ) -> imdb_top_250_new

imdb_top_250_new

```


Writing the tibble to csv
```{r}
# Load the readr package
library(readr)


# Tibble to write
my_tibble <- imdb_top_250_new

# Define the path where you want to save the CSV file
file_path <- "/home/silas/top_250_movies_new.csv"

#Notice the path includes a file name

# Write the tibble to a CSV file
write_csv(my_tibble, file_path)

```



